Baseline centering problem

### 2018-11-24 paper/tangotd.tex

A few choices are:
\begin{itemize}
\item $B=A^{-1}$: obviously stable, jumps to the solution in one step if
$\eta=1$. Requires computing the inverse of $A$, namely, solving the
problem.
\end{itemize}

>>>>

A few choices are:
\begin{itemize}
\item $B=A^{-1}$: obviously stable, jumps to the solution in one step if
$\eta=1$. Requires computing the inverse of $A$, namely, solving the
problem. But if $A$ is stable and samplable, this can be done via TANGO.

\item $B=(\transp{\Phi}\rho\Phi)^{-1}$. Then we have to prove that
$(\transp{\Phi}\Phi)^{-1}\transp{\Phi}\rho(\Id-P)\Phi$ is stable. Taking
$L=\transp{\Phi}(\mu/\rho)\Phi$, and computing
\begin{align}
\transp{\theta}LBA\theta&=
\transp{\theta}L(\transp{\Phi}\rho\Phi)^{-1}\transp{\Phi}\rho(\Id-P)\Phi\theta
\end{align}
and note that $(\transp{\Phi}\rho\Phi)^{-1}\transp{\Phi}\rho$ is the
solution of linear regression with design matrix $\Phi$ in $L^2(\rho)$.
This implies that
\begin{equation}
\Phi(\transp{\Phi}\rho\Phi)^{-1}\transp{\Phi}\rho=\Pi_\Phi
\end{equation}
where $\Pi$ is the orthogonal projector on the image of $\Phi$ in
$L^2(\rho)$. Now taking
\begin{equation}
L=\transp{\Phi}(\mu/\rho)\Phi
\end{equation}
we have
\begin{equation}
\transp{\theta}LBA\theta=\transp{\theta} \transp{\Phi}(\mu/\rho)\Pi_\Phi
(\Id-P)\Phi\theta
\end{equation}
\end{itemize}
